The Future of Global Fishery Assessments

### 2020-07-23 documents/ovando-etal-assessing-global-fisheries.Rmd
results with updatede priors, no real changes

---
title: "The Future of Global Fishery Assessments"
author: 
  - Daniel Ovando
  - Ray Hilborn
  - Cole Monnahan
  - Merrill Rudd
  - Rishi Sharma
  - James Thorson
  - Yimin Ye
date: "`r Sys.Date()`"
bibliography: ["../references.bib"]
csl: nature.csl
output: 
  bookdown::word_document2: default
  bookdown::pdf_document2: default
abstract: Assessments of the global state of fisheries play an important role in shaping the public narrative around ocean health, motivating future directions of research and funding, and tracking large-scale objectives such as the United Nations Sustainable Development Goals. Numerous high-profile publications have produced estimates of the global status of fisheries, but limited quantity and quality of data, conflicting results, and methodological concerns mean that our understanding of global fisheries is still highly uncertain, especially in critical areas such as Southeast Asia and Africa. We present an evaluation of the past and future of global fishery assessments. Global assessments have typically involved aggregating best-available stock assessments where possible with various data-limited assessments for regions lacking formal evaluations of stock status. The data-limited methods used have ranged from simple catch heuristics to super-ensemble modeling. Despite attempts at model improvement, there have been discrepancies both among global fishery assessments and between the data-limited components of these methods and more data-rich models,demonstrating that our understanding of global data-limited fisheries remains limited. How then can we most efficiently move forward? We utilize a flexible assessment model together with the RAM Legacy Stock Assessment Database not strictly as a stock assessment tool, but to assess the value of different kinds, quantities, and quality of data in improving estimates of fishery stock status. We then explore avenues for obtaining potentially impactful data, including through the use of local expert opinion and increasingly available but historically underutilized data such as trawl footprints. These data are then used to illustrate how different types of information paint starkly different pictures of the state of fisheries around the world. We close by discussing priority areas for future data collection. Our results make the case that improving our understanding of global fisheries depends not on better models, but on better data.
---

@@

*Insert mandatory opening sentence about the importance of global fisheries*. The United Nations Sustainable Development Goal 14 calls for the global community to "Conserve and sustainably use the oceans, seas and marine resources for sustainable development". A substantial part of achieving this goal rests on ensuring that marine fisheries are managed levels that ensure the conservation and sustainable use of ocean ecosystems. Achieving this goal depends in part on our ability to effectively track the status of global marine fish stocks. The Food and Agriculture Organization of the United Nations' (FAO) State of World Fisheries and Aquaculture (SOFIA) report is the standard source for tracking this important metric. As of the most recent report, the FAO estimates that as of 2017 59.6% of marine fish stocks are maximally sustainably fishery, 6.2% are underfished ,and 34.2% are overfished [@fao2020].

However, there are two major areas of improvement needed to ensure that we are able to accurately track the status of global fisheries. XX% of the global landings covered by the SOFIA reports come from fisheries with formal statistical stock assessments, quantitative models that provide estimates of stock status based on the best available science. These stock assessments are then incorporated into the SOFIA report's estimates of global stock status. The remaining XX% of the stocks/landings covered by SOFIA lack formal stock assessments. For these important fisheries, FAO scientists must use a mixture of local expert knowledge, data synthesis, and expert opinion to infer stock status. While this process provides the best available estimate of stock status, ideally a more reproducible  XX something to communicate why we might want to improve things for these stocks XX.

Second, there are many fisheries that while perhaps small on a global scale provide critical ecosystem services to their adjacent communities. These fisheries collectively, making up XX% of global landings, are not contained in the FAO assessment, but still fall under the SDG 14 goal XX to what extent is this true?  XX rishi would be good to work on this section together. By my count the total catch form the SOFIA table sent to me is 42.68 MMT, so about half of global catch, but SOFIA 2020 says that "78.7 percent of current landings come from biologically sustainable stocks.", which would imply then that basically all landings are in SOFIA (since that doesn't leave much room for the assessed but overfished)? Confused by discrepancy hereXX.

Ideally, both of these problems would be solved by simply running formal stock assessments on all significant fisheries. This is rendered impossible though both by lack of data and human resources. Formal stock assessment require at a minimum robust timeseries of captures and a reliable index of abundance such as catch-per-unit-effort (CPUE). While most of the world's largest and most valuable fisheries have these data and have stock assessments based on the data [@hilborn2020], for many of the world's fisheries these data do not exist, and would be prohibitively expense to collect. Even when data are available though, running an individualized stock assessment is not a "just press play" process. Assessment scientists must make careful considerations about the quality and subsequent weighting of available data, the level of biological abstraction that the species and the data can support in the assessment model, and of course the quality of results produced by the assessment. This process takes considerable time and expertise. As such, effectively tracking the status of all global fisheries will require alternative methods.

To resolve this problem, numerous papers have developed methods that while not intended for the management of individual stock are hoped to provide reasonable estimates of stock status in aggregate, particularly for those regions lacking the data or capacity for formal stock assessment. These include @costello2016a, @rosenberg2018, and @pauly2007. Each of these methods sought to address specific gaps in our understanding of global fisheries, and in doing so introduced unique strengths and weaknesses. While not suitable for management of individual stocks, these broad strategic models have played an important role in shaping the public narrative around ocean health.

However, comparing estimates from each of these methods against best-available knowledge of stock status from the RAM Legacy Stock Assessment Database [@ricard2012], as well as broader intuition. reveals some systemic problems with these assessments. We have stock assessment data from RAM from the NE Pacific,the NE Atlantic and the Mediterranean, and of these the NE Pacific is in the best state (mean RAM B/B~MSY~ =1.8), NE Atlantic (mean RAM B/B~MSY~ =1.3) and the Mediterranean the worst (mean RAM B/B~MSY~ =0.5).  We do not have formal stock assessment data from S. and SE Asia (Western Central Pacific and Eastern Indian Ocean), but based on surveys and expert opinion we believe it should be worse than Northeast Pacific. The Costello et al. 2016 [@costello2016a] model shows the correct general pattern, but we would expect the state of fisheries in the Mediterranean/Black sea regions and SE Asia to be much worse, and the NE Pacific better by comparison. The Rosenberg super-ensemble method[@rosenberg2018] demonstrates the same problem, with stocks in SE Asia estimated as doing better than the NE Atlantic or NE Pacific. The catch based approach @pauly2007, which compares catch in the last year to maximum catch, finds the stocks of Southeast Asia in much better condition than the Northeast Pacific or Northeast Atlantic (Table.\@ref(tab:status-tab)) *probably want to make this a figure. Also, Ray, do you remember if these estimates are unassessed only, or unassessed + RAM?*

@@

The coming decades are a critical period for the future of global oceans. Climate change, population growth, and economic expansion will all place increasing pressure on fisheries. Mitigating these threats, as called for by SDG 14, will require an improved ability to track the status of fisheries around the world. At the same time, new sets of globally distributed data have recently become available, along with advances in statistical modeling methods. We leverage these opportunities to provide a global assessment of our perception of global stock status resulting from different use of different data sources. Our results demonstrate that modeling improvements alone cannot provide a satisfactory answer to the question of global fishery status, requiring instead a robust and worldwide data collection and interpretation effort.

@@

The FAO's catch statistics remain the most widely accessible and used source of information on global fisheries. Several methods have attempted to infer stock status (generally biomass relative to biomass at maximum sustainable yield, B/B_msy_) based on a fishery's catch history alone [summarized by @free2020]. However, these "catch-only" methods have serious shortcomings that limit their performance, as evidenced by the status discrepancies by region they produce (Table.\@ref(tab:status-tab)), as well as results from several studies examining the performance of such methods [@free2020; @pauly2013].

However, catches are not the only broadly available source of fishery data. We augment the FAO's catch statistics with broadly distributed data on fishing effort [@rousseau2019], strength of management [@anderson2015], trawl-fishing footprints [@amoroso2018], and life history [@thorson2017c]. We use a flexible assessment package ([sraplus](https://github.com/DanOvando/sraplus#sraplus)) to compare estimates of stock status around the globe using different combination of these data.

@@

Evaluating the validity of data-limited XX need to introduce this idea earlier xx assessment methods can be a challenging task. Simulation testing provides one avenue, but can be difficult to create a simulation environment that adequately captures the problems of real-world ecosystems and data. We can also compare results between data-limited assessment and more data (or resource) rich gold-standard stock assessments. However, formally stock asssessed fisheries represent a very biased subset of global fisheries, and it is entirely possible that a method that performs well for the kinds of species and fisheries that are commonly stock assessed might struggle in the kinds of fisheries that typically are unassessed.

Alternatively though, while we may lack formal assessment for many regions of the world, stakeholders familiar with a region often have a general sense of the state of fisheries in a region. As outlined in Table.1, while we often have no proof that results finding that for example fisheries in south-east Asia have similar stock status to those in Alaska, very few experts would agree that this is a plausible result XX tough statement to make in a paper xx. We use two case studies here to present the potential of additional, broadly applicable, data to potentially improve on "catch-only" methods.

For our first case study, we augment local catch statistics from the Eastern Bay of Bengal (XX details on these data) with catch-per-unit effort data from a local study, as well as a local estimate of swept-area-ratio for the region. We can then compare the estimates of stock status that come from using the catch-data alone (with a heuristic algorithm in the manner of @martel2013), with the catch data along with priors on terminal depletion informed by the swept-area-ratio data, and using the swept-area ratio data together with a local abundance index. By it's nature the catch-only heuristic produces a bi-model distribution, with most fisheries reported to have a B/B~MSY~ of 1.5 and an F/F~MSY~ less than 1 (Fig.\@ref(fig:east-india)-heuristic). Local experts put the swept-area-ratio (SAR) value for the region at an incredibly high 17. Using this value to inform a prior on terminal stock status dramatically changes our picture of stock status in the Eastern Bay of Bengal, with now all stocks being overfished and experiencing high levels of overfishing (Fig.\@ref(fig:east-india)-sar).

@@

It should be no surprise that incorporating locally tailored data produces more locally plausible results. Global assessment at the moment though requires depending on a few broadly available datasets. To give an illustration, we used `sraplus` to assess the status of in Europe and Northeast Asia using catch data from the FAO augmented with regional effort indices constructed from @rousseau2019 (xx technically this is the updated dataset xx). Interestingly, catch histories for Europe and Northeast Asia look somewhat similar xx plot of catch and effort histories xx. As a result, using a "catch-only" heuristic, both Europ and Northeast Asia are estimated to have very similar stock status, a similar finding as those illustrated in Table.XX. Adding in the effort data (as an effort index created for each stock as catch divided by the effective harvest rate based on the effort data), and the two regions begin to diverge. While according to @rousseau2019, Europe has seen a recent decrease in fishing effort from a peak in XX, effort in Northeast Asia has increased more or less continuosly. As a result, `sraplus` estimates that more stocks in Northeast Asia are overfished / experiencing overfishing than in Europe. However, the shared effort series across these stocks aslo produces a large number of effectively unfished stocks; a highly unlikely result for both regions.

@@

Our results show that our perception of global fishery depends completely on which data sources we utilize. That different data tell different stories should not be surprising. However, we also do not see a convergence towards a cohesive picutre of global status that closely matches the SOFIA report as we add more data. The most data-poor method employed, the catch heuristic alone, matches some patterns from the SOFIA report (little overfishing in the Northeast Pacific, some overfishing in the northwest Atlantic), it misses the mark badly in other regions, e.g. the waters around New Zealand. Our most data-rich scenario, an effort series from @rousseau2019, along with priors from swept-area-reatio and fisheries management index where available....

@@

Global-level assessment are critical for guiding management agendas for the world's oceans. Despite this need, and despite advances in stock assessment methods, our understanding of many of the world's fisheries remains poor. We show that while new sources of widely available data are becoming increasingly available, none yet is capable of providing a clear improvement in our estimates of global stock status.

Our estimate of global stock status varies wildly depending on which source of data we use. Why not simply pick the best source of data, or use all the available data, and use that to update our estimate of global stock status? Unfortunately, it is not clear that we can evaluate which source of data provides the best fit; examination of each shows strengths and weakness that are not easily comparable (Fig.\@ref(fig:po-map)). Globally available effort data from Rousseau allows us to create local indices of abundance based on catch histories but carries a host of critical assumptions, namely that the same effort history applies to all fisheries in the region. These CPUE indices are also extremely sensitive to assumptions around rates of change in catchability. The fisheries management index has some ability in predicting stock status (Fig.XX), but out-of-sample testing reveals limitations. Swept-area ratios have a strong relationship with fishing mortality rates, but only for comparable fisheries; it is unclear how good a proxy this measure is for non-demersal stocks.

We have stated that improving global estimates of stock status depends on improved data, not improved models *per say*. This is not to suggest that improvements in stock assessment methods, even for relatively simple models such as the biomass dynamics types used here, are not of use. At the tactical level, such improvements can make meaningful changes in management outcomes. However, at the global strategic levels, the improvements to be made from model development are marginal compared to the fundamental uncertainties stemming from currently available data.

What does the future of global fishery assessment look like? Investment must be made in improving data collection at the global scale. Our analysis suggests several possible paths for this process, in particular creation of a global repository or length-composition data, and expansion of FMI surveys and SAR data. Global Fishing Watch provides another avenue, but requires further research on the best ways of translating raw effort data into indices of stock status. Interpreting these data responsibly will require support from regional experts, for example in the form of expert panels charged with determine the most representative broadly available data for different portions of the oceans.

@@

XX equations here XX.

>>>>

---
title: "The Future of Global Fishery Assessments"
author: 
  - Daniel Ovando
  - Ray Hilborn
  - Cole Monnahan
  - Merrill Rudd
  - Rishi Sharma
  - James Thorson
  - Yimin Ye
date: "`r Sys.Date()`"
bibliography: ["../references.bib"]
csl: nature.csl
output: 
  bookdown::word_document2:
    reference_docx: word-template.docx
  bookdown::pdf_document2: default
abstract: |
  Assessments of the global state of fisheries play an important role in shaping the public narrative around ocean health, motivating future directions of research and funding, and tracking large-scale objectives such as the United Nations Sustainable Development Goals. Numerous high-profile publications have produced estimates of the global status of fisheries, but limited quantity and quality of data, conflicting results, and methodological concerns mean that our understanding of global fisheries is still highly uncertain, especially in critical areas such as Southeast Asia and Africa. We present an evaluation of the past and future of global fishery assessments. Global assessments have typically involved aggregating best-available stock assessments where possible with various data-limited assessments for regions lacking formal evaluations of stock status. The data-limited methods used have ranged from simple catch heuristics to super-ensemble modeling. Despite attempts at model improvement, there have been discrepancies both among global fishery assessments and between the data-limited components of these methods and more data-rich models,demonstrating that our understanding of global data-limited fisheries remains limited. How then can we most efficiently move forward? We utilize a flexible assessment model together with the RAM Legacy Stock Assessment Database not strictly as a stock assessment tool, but to assess the value of different kinds, quantities, and quality of data in improving estimates of fishery stock status. We then explore avenues for obtaining potentially impactful data, including through the use of local expert opinion and increasingly available but historically underutilized data such as trawl footprints. These data are then used to illustrate how different types of information paint starkly different pictures of the state of fisheries around the world. We close by discussing priority areas for future data collection. Our results make the case that improving our understanding of global fisheries depends not on better models, but on better data.
---

@@

The United Nations Sustainable Development Goal 14, related to "Life under water", calls for the global community to "Conserve and sustainably use the oceans, seas and marine resources for sustainable development". A substantial part of achieving this goal rests on ensuring that marine fisheries are managed to levels that ensure the conservation and sustainable use of ocean ecosystems. Achieving this goal depends in part on our ability to effectively track the status of global marine fish stocks. The Food and Agriculture Organization of the United Nations' (FAO) State of World Fisheries and Aquaculture (SOFIA) report is the standard source for tracking this important metric. As of the most recent report, the FAO estimates that as of 2017 59.6% of marine fish stocks are maximally sustainably fishery, 6.2% are underfished ,and 34.2% are overfished [@fao2020].

However, there is room for substantial improvement in the methods used in estimating global stock status. 49% of landings of marine fishes reported by the FAO are represented in the RAM Legacy Stock Assessment Database, a repository of "gold standard" estimates of fishery status [@hilborn2020]. The SOFIA process uses these formal assessments for their determinations of stock status wherever possible. However, that leaves 51% of global fisheries landings lacking in formal stock assessments. While these "unassessed" stocks are generally individually smaller than the typically larger and more valuable stocks in the assessed category, collectively they are a vital source of food, employment, cultural value, and ecosystem services around the world.

The SOFIA report bases its estimates of included unassessed stocks mostly on expert elicitation. While local experts often are well informed as to the status of their fish stocks, a more quantitative and reproducible process would be desirable. Numerous studies in recent years have put forward versions of "data-limited" models that have attempted to provide estimates for the global status of these unassessed stocks [@costello2012;@costello2016a;@rosenberg2018;@pauly2007].Formal stock assessment require at a minimum robust timeseries of captures and a reliable index of abundance such as catch-per-unit-effort (CPUE). While most of the world's largest and most valuable fisheries have these data and have stock assessments based on the data [@hilborn2020], for many of the world's fisheries these data do not exist, and would be prohibitively expense to collect. Even when data are available though, running an individualized stock assessment is not a "just press play" process. Assessment scientists must make careful considerations about the quality and subsequent weighting of available data, the level of biological abstraction that the species and the data can support in the assessment model, and of course the quality of results produced by the assessment. This process takes considerable time and expertise.

Data-limited methods applied to the question of global stock status typically make compromises on both the data requirements and individual attention needed for formal stock assessment. Given that catch statistics are, to date, the only globally available form of comparable fishery data, global data-limited assessments have typically been forms of "catch-only" models [@free2020 and references therein]. These models seek to infer stock status, for example in terms of biomass *b* relative to the biomass at maximum sustainable yield *b~MSY~*, from characteristics of a fishery's catch history, for example the ratio of catch to maximum catch [@martell2013]. In addition, given that a global assessment by its nature requires producing results for hundreds or thousands of individual fisheries within a reasonable amount of time. As such, rather than spending time carefully evaluating the quality of the data, model assumptions, and model fit for individual stocks, global data-limited methods typically aim for a method that is on average correct, but may not be reliable for assessment of individual stocks (high variance, low bias).Each of these methods sought to address specific gaps in our understanding of global fisheries, and in doing so introduced unique strengths and weaknesses.

However, @free2020 demonstrated that these catch-only models can often produce both imprecise and biased estimates of B/B~MSY~. These issues become apparent when we consider some of the macro-level predictions made by these models. Examining stock assessment data from RAM from the NE Pacific, the NE Atlantic and the Mediterranean, the NE Pacific is in the best state (mean RAM b/b~MSY~ = 1.8), NE Atlantic (mean RAM b/b~MSY~ =1.3) and the Mediterranean the worst (mean RAM b/b~MSY~ =0.5).  We do not have formal stock assessment data from S. and SE Asia (Western Central Pacific and Eastern Indian Ocean), but based on surveys and expert opinion we believe it should be worse than Northeast Pacific. The Costello et al. 2016 [@costello2016a] model shows the correct general pattern in terms of relative ranking of regions, but we would expect the state of fisheries in the Mediterranean/Black sea regions and SE Asia to be much worse, and the NE Pacific better by comparison. The Rosenberg super-ensemble method [@rosenberg2018] demonstrates the same problem, with stocks in SE Asia estimated as doing better than the NE Atlantic or NE Pacific. The catch based approach @pauly2007, which compares catch in the last year to maximum catch, finds the stocks of Southeast Asia in much better condition than the Northeast Pacific or Northeast Atlantic (Table.\@ref(tab:status-tab)).

@@

The coming decades are a critical period for the future of global oceans. Climate change, population growth, and economic expansion will all place increasing pressure on fisheries. While our understanding of global fisheries has improved greatly,  mitigating these threats, as called for by SDG 14, will require an improved ability to track the status of fisheries around the world, particularly those stocks that are currently unassessed. At the same time, new sets of globally distributed data have recently become available, along with advances in statistical modeling methods. We leverage these opportunities to provide a global assessment of our perception of global stock status resulting from different use of different data sources. Our results demonstrate that modeling improvements alone cannot provide a satisfactory answer to the question of global fishery status, requiring instead a robust and worldwide data collection and interpretation effort.

@@

We use a new assessment package, [`sraplus`](www.github.com/danovando/sraplus) to demonstrate how different sources data can be used to augment catch-only models at a global scale, and to evaluate how our perception of global stock status would vary depending on which sources of data we include. The FAO's catch statistics remain the most widely accessible and used source of information on global fisheries. However, catches are not the only broadly available source of fishery data. We augment the FAO's catch statistics with broadly distributed data on fishing effort [@rousseau2019], strength of management [@anderson2015], trawl-fishing footprints [@amoroso2018], and life history [@thorson2017c]. `sraplus` provides a flexible framework for integrating these data into valid statistical model. `FishLife` [@thorson2017c] provides informative priors for key life history parameters (such as growth rates) needed by our model. We use the FMI and SAR values to construct Bayesian priors on initial and terminal stock status values (e.g B/B~MSY~ or F/F~MSY~, the fishing mortality *F* relative to the fishing mortality rate that would produce *MSY* at equilibrium), allowing us to translate local values of for example SAR into a prior on terminal B/B~MSY~. Where available, we use effort data to create stock-specific timeseries of catch-per-unit-effort (CPUE), which can be used as an index of stock abundance.

@@

Two case studies provide examples of how augmenting catch data alone with local and globally available data can provide dramatically different estimates of local stock status. For our first case study, we augment local catch statistics from the Eastern Bay of Bengal (XX details on these data) with catch-per-unit effort data from a local study, as well as a local estimate of swept-area-ratio for the region. We can then compare the estimates of stock status that come from using the catch-data alone (with a heuristic algorithm in the manner of @martel2013), with the catch data along with priors on terminal depletion informed by the swept-area-ratio data, and using the swept-area ratio data together with a local abundance index. By it's nature the catch-only heuristic produces a bi-model distribution, with most fisheries reported to have a B/B~MSY~ of 1.5 and an F/F~MSY~ less than 1 (Fig.\@ref(fig:east-india)-heuristic). Local experts put the swept-area-ratio (SAR) value for the region at an incredibly high 17. Using this value to inform a prior on terminal stock status dramatically changes our picture of stock status in the Eastern Bay of Bengal, with now all stocks being overfished and experiencing high levels of overfishing (Fig.\@ref(fig:east-india)-sar).

<!-- Evaluating the validity of data-limited assessments methods can be challenging. Simulation testing provides one avenue, but it can be difficult to create a simulation environment that adequately captures the problems of real-world ecosystems and data. We can also compare results between data-limited assessment and more data (or resource) rich gold-standard stock assessments. However, formally stock assessed fisheries represent a very biased subset of global fisheries, and it is entirely possible that a method that performs well for the kinds of species and fisheries that are commonly stock assessed might struggle in the kinds of fisheries that typically are unassessed.  -->

<!-- Alternatively though, while we may lack formal assessment for many regions of the world, stakeholders familiar with a region often have a general sense of the state of fisheries in a region. As outlined in Table.\@ref(tab:status-tab), while we often have no proof that results finding that for example fisheries in south-east Asia have similar stock status to those in Alaska, very few experts would agree that this is a plausible result XX tough statement to make in a paper xx. We use two case studies here to present the potential of additional, broadly applicable, data to potentially improve on "catch-only" methods.  -->

@@

It should be no surprise that incorporating locally tailored data produces more locally plausible results. Global assessment at the moment though requires depending on a few broadly available datasets. To give an illustration, we used `sraplus` to assess the status of in Europe and Northeast Asia using catch data from the FAO augmented with regional effort indices constructed from @rousseau2019 (xx technically this is the updated dataset xx). Catch histories for Europe and Northeast Asia look somewhat similar xx plot of catch and effort histories xx. As a result, using a "catch-only" heuristic, both Europ and Northeast Asia are estimated to have very similar stock status, a similar finding as those illustrated in Table.XX. Adding in the effort data (as an effort index created for each stock as catch divided by the effective harvest rate based on the effort data), and the two regions begin to diverge. While according to @rousseau2019, Europe has seen a recent decrease in fishing effort from a peak in XX, effort in Northeast Asia has increased more or less continuosly. As a result, `sraplus` estimates that more stocks in Northeast Asia are overfished / experiencing overfishing than in Europe. However, the shared effort series across these stocks aslo produces a large number of effectively unfished stocks; a highly unlikely result for both regions.

@@

Our perception of global fishery depends completely on which data sources we utilize. That different data tell different stories should not be surprising. However, we also do not see a convergence towards a cohesive picture of global status that closely matches the SOFIA report as we add more data. The most data-poor method employed, the catch heuristic alone, matches some patterns from the SOFIA report (little overfishing in the Northeast Pacific, some overfishing in the northwest Atlantic), it misses the mark badly in other regions, e.g. the waters around New Zealand. Our most data-rich scenario, an effort series from @rousseau2019, along with priors from swept-area-reatio and fisheries management index where available....

@@

Global-level assessment are critical for guiding management agendas for the world's oceans. Despite this need, and despite advances in stock assessment methods, our understanding of the world's fisheries remains murky in many parts of the world. Numerous efforts have sought to resolve this problem through development of new modeling methods. These studies have ranged from simple heuristic algorithms to superensemble modeling, but while these studies have advanced our knowledge and motivated important conversations about the state of unassessed fisheries, each has demonstrable shortcomings as an answer for global fisheries assessment. This project was motivated by the need to address this problem, and the increasing availability of broadly (if not globally) datasets that could be of use for fisheries assessment. While we demonstrate that these data can provide value above and beyond the catch histories alone, addition of these data alone does not substantially clarify the picture of global fisheries status.

Our estimates of global stock status vary wildly depending on which source of data we use. Why not simply pick the best source of data, or use all the available data, and use that to update our estimate of global stock status, under the grounds that that is the best available information? Unfortunately, it is not clear that we can evaluate which source of data provides the best fit; examination of each shows strengths and weakness that are not easily comparable (Fig.\@ref(fig:po-map)). Globally available effort data from Rousseau allows us to create local indices of abundance based on catch histories but carries a host of critical assumptions, namely that the same effort history applies to all fisheries in the region. These CPUE indices are also extremely sensitive to assumptions around rates of change in catchability. The fisheries management index has some ability in predicting stock status (Fig.XX), but out-of-sample testing reveals limitations. Swept-area ratios have a strong relationship with fishing mortality rates, but only for comparable fisheries; it is unclear how good a proxy this measure is for non-demersal stocks. None of these data, or combinations thereof, was able to satisfactorily match the FAO's SOFIA assessments, or the assessments presented in RAM (XX RAM matches? need to add an analysis: match stocks from SOFIA to RAM stocks where possible, plot comparison).

This is not to say that the data presented here are not valuable. The FMI and SAR based priors are an improvement over catch-only models in applicable situations (i.e. those that sufficiently resemble the data on which the regressions were trained). Effort data such as those reconstructed by @rousseau2019a can help distinguish between regions with similar catch histories but different effort trajectories, and may be quite useful as indices of abundance for areas with relatively constant fishing technologies and a broadly selective fishing fleet. The challenge comes in attempting to indiscriminately apply these data to all areas: doing so results in substantially incorrect estimates of stock status for regions whose nature does not match the assumptions needed to apply these data sources.

We have stated that improving global estimates of stock status depends on improved data, not improved models *per say*. This is not to suggest that improvements in stock assessment methods, even for relatively simple models such as the biomass dynamics types used here, are not of use. We certainly do not claim that the modeling choices we have made here represent the best version possible. At the tactical level, modeling improvements can make meaningful changes in management outcomes. However, at the global strategic level, the evidence from multiple efforts at assessing global fisheries strongly suggests that any improvements to be made from model improvement are marginal compared to the fundamental uncertainties stemming from currently available data.

What does the future of global fishery assessment look like? Investment must be made in improving  global data collection and training local fisheries scientists. While the data used in this study were not a silver bullet, they present a step forward, and local versions of these data could prove immensely helpful. Stock-specific, as opposed to the often broad regional estimates used here, estimates of swept-area-ratio and fisheries management index scores can provide improved priors on stock status for applicable fisheries. Informative priors on fishing mortality rates can be particularly useful in improving accuracy of data-limited assessment results (Fig.XX VOI XX)

Our analysis suggests several possible paths for this process, in particular creation of a global repository or length-composition data, and expansion of FMI surveys and SAR data. Global Fishing Watch provides another avenue, but requires further research on the best ways of translating raw effort data into indices of stock status. Interpreting these data responsibly will require support from regional experts, for example in the form of expert panels charged with determine the most representative broadly available data for different portions of the oceans.

@@

```{r}
cd <- data_frame(Parameter = "Carrying Capacity", Abbreviation = "K", `Default Prior` = "$logn(10\\times{max(catch)},4)$") %>%
  rbind(c("Growth rate", "r", "$logn(r_{fishlife}, \\sigma_{r,fishlife})$")) %>%
  rbind(c("Shape parameter", "m", "$logn(1.01, 0.25)$")) %>%
  rbind(c("Catchability", "q", "$logn(1e^{-3}, 0.3)$")) %>%
  rbind(c("Observation Error", "$\\sigma_{obs}$", "$logn(.05,2)$")) %>%
  rbind(c("Process Error", "$\\sigma_{proc}$", "$logn(.05,0.5)$")) %>% 
  rbind(c("Tech Creep", "$creep$", "$logn(0.025,0.2)$"))

knitr::kable(
  cd,
  "latex",
  align = "l",
  booktabs = TRUE,
  escape = F,
  row.names = F,
  caption = "Estimated parameters, abbreviations, and default priors"
) %>%
  kableExtra::kable_styling(full_width = T, font_size = 9) %>%
  kableExtra::row_spec(0, bold = T)
```

The population growth equation is

\begin{equation}
  f(x)=\begin{cases}
      B_{t + 1} = \left(B_{t} + B_{t}\frac{r}{m - 1}\left(1 - \left(\frac{B_t}{K}\right)^{m- 1}\right) - \hat{c_t}\right)p_t
, & \text{if $B_t>0.25 \times K$}.\\
     B_{t + 1} = \left(B_{t} + \frac{B_{t}}{0.25 \times K}\left(B_{t}\frac{r}{m - 1}\left(1 - \left(\frac{B_t}{K}\right)^{m- 1}\right) - \hat{c_t}\right)\right)p_t, & \text{otherwise}.
  \end{cases}
  (\#eq:hockey)
\end{equation}

Where $B_t$ is biomass at time *t*, *r* is the intrinsic growth rate, *m* is the scaling parameter that allows for the ratio of Bmsy/K to shift (when *m* is 2 the Bmsy / K = 0.5 and the model acts as a Schaefer model, lower values of m shift the production function left, higher values right), *c* is catch, and *p* is process error. The Pella-Tomlinson model does have an issue where growth rates can become unrealistically large when the population reaches low sizes. We deal with this problem by following the methods described in @winker2018 to reduce the production of the population when it falls below a threshold of 25% of carrying capacity. Incorporation of process errors is useful for two reasons: (1) when you have an abundance index, process errors can reduce bias arising from lack of fit in a deterministic SRA whenever dynamics are poorly explained by catch-history alone, and (2) with or without an abundance index (or other info), the stochastic portion is necessary to get good uncertainty intervals (i.e., with close to nominal coverage, see @thorson2018).

<!-- When the SIR method is used we use the supplied catch history. However, for the maximum likelihood approach, convergence is greatly facilitated by estimating catches ($\hat{c_t}$) rather than using the observed catches directly. $\hat{c_t}$ is given as -->

<!-- \begin{equation} -->
<!--   \hat{c_t} = u_{t}B_{t} -->
<!--   (\#eq:chat) -->
<!-- \end{equation} -->

<!-- where $u_t$ is estimated through -->

<!-- \begin{equation} -->
<!--   u_{t} = \frac{1}{1 + e^{-u^*_t}} -->
<!--   (\#eq:invf) -->
<!-- \end{equation} -->

<!-- Equation \@ref(eq:invf) ensures that $u_t$ is between 0 and 1, while the model estimates $u^*_t$ to improve performance.  -->

<!-- $\hat{c_t}$ is then fit to the observed catches through the likelihood -->

<!-- \begin{equation} -->
<!--   log\left(c_t\right) \sim normal\left(log\left(\hat{c_t}\right),0.05\right) -->
<!--   (\#eq:catch) -->
<!-- \end{equation} -->

<!-- Where we assume an observation coefficient of variation of 5\%. We estimate catch rather than directly using the observed catch in order to improve model performance. As priors on depletion, or indices of abundance, pull the estimated population closer to zero, there is a greater and greater chance that the observed catch history will result in a collapse of the population (catch in time *t* being greater than biomass in time *t*); It is much harder to find parameters that produce a final depletion of 1\% of carrying capacity while not crashing the population prior to then given a catch history, than it is to produce a final depletion of 99\% of carrying capacity. We can impose restrictions and penalties on population crashes, but this distorts the gradients of the model, causing the model to often become stuck once a few crashes have occurred. Since $u_t$ is constrained between 0 and 1, $\hat{c_t}$ will always be "viable", and by then fitting to the observed catches, the model has an easier time finding parameters that produce a near match to the observed catches while not crashing the population. As of now none of the data used in this exercise have missing years of catch data, but the model can handle those cases in the future due to the random walk priors imposed on $u_t$ detailed below.  -->

<!-- In order to help separate out observation error in the catch and process error in the population model, when catch is being estimated we assume that fishing mortality $u_t$ follows a random walk on average, assigning each $u_t$ a prior of -->

<!-- \begin{equation} -->
<!--   log(u_t) \sim normal(log(u_{t - 1}),0.1)) -->
<!--   (\#eq:rwalk) -->
<!-- \end{equation} -->

We  allow for process error [in the manner of the stochastic stock reduction analysis error suggested by @walters2006]. This allows the population dynamics to deviate from the exact values given by the Pella-Tomlinson operating model, while still conforming to the assumptions of this model on average. Process error *p* is assumed to be log-normally distributed, such that

\begin{equation}
  p_t \sim e^{normal\left(-\sigma_{proc}^2/2,\sigma_{proc}\right)}
  (\#eq:procerror)
\end{equation}
